---
title: "Map_Work"
author: "Philipp Hoeper"
date: "02/05/2020"
output: html_document
---

```{r}
library(tidyverse)
library(glue)
library(plotly)
library(dygraphs)
library(xts)
library(reactable)
library(lubridate)
```

## Importing Data

```{r}
base_url <-
  paste0(
    "https://raw.githubusercontent.com/CSSEGISandData",
    "/COVID-19/master/csse_covid_19_data/",
    "csse_covid_19_daily_reports/"
  )

## currently just one dayb:
date_latest <-"04-25-2020"

extension <- ".csv"

url <- paste0(base_url, date_latest, extension)

daily <- read_csv(file = url) %>% 
  rename(country_or_region = "Country_Region") %>% 
  rename(Province_or_State = "Province_State")
```

COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series
https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series
base_url <-
  paste0('https://raw.githubusercontent.com/',
         'CSSEGISandData/COVID-19/master/',
         'csse_covid_19_data/csse_covid_19_time_series/')



```{r}
base_url <-
  paste0('https://raw.githubusercontent.com/CSSEGISandData',
    '/COVID-19/master/csse_covid_19_data/',
         'csse_covid_19_time_series/')

filename <- 
  paste0('time_series_covid19_', 
         c('confirmed_global', 'deaths_global', 'recovered_global'), '.csv')


url <- paste0(base_url, filename)
url
```
Confirmed <- url[1] %>% 
  read_csv(col_types = cols(
    .default = col_double(),
    `Province/State` = col_character(),
    `Country/Region` = col_character()
  )) %>%
  rename(country_or_region = `Country/Region`)

```{r}
Confirmed <- url[1] %>% 
  read_csv(col_types = cols(
    .default = col_double(),
    `Province/State` = col_character(),
    `Country/Region` = col_character()
  )) %>%
  rename(country_or_region = `Country/Region`)

Deaths <- url[2] %>% 
  read_csv(col_types = cols(
    .default = col_double(),
    `Province/State` = col_character(),
    `Country/Region` = col_character()
  )) %>%
  rename(country_or_region = `Country/Region`)

Recovered <- url[3] %>% 
  read_csv(col_types = cols(
    .default = col_double(),
    `Province/State` = col_character(),
    `Country/Region` = col_character()
  )) %>%
  rename(country_or_region = `Country/Region`)
```





```{r}
reactable::reactable(daily, searchable = TRUE,
                     pageSizeOptions = c(5, 10, 20), 
                     defaultPageSize = 5)
```

```{r}
extra <- c(
  "Guam", "Grand Princess", "Virgin Islands, U.S.",
  "Diamond Princess", "Puerto Rico"
)
us <-
  us %>% 
  filter(!(Province_or_State %in% extra))
```

```{r}
data("statepop", package = "usmap")
glimpse(statepop)
```

```{r}
us <-
  us %>% 
  rename(full = Province_or_State) %>% 
  inner_join(statepop, by = "full") %>% 
  select(fips, abbr, full, Confirmed, Deaths, Recovered) %>% 
  mutate(hover = glue::glue(
    "{full}
     Deaths: {Deaths}
     Recovered:  {Recovered}"
  ))
```


```{r}
# give state boundaries a red border
lcol <- list(color = toRGB("red"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

fig <- plot_geo(us, locationmode = 'USA-states',
                marker = list(line = lcol))
fig <- fig %>% add_trace(
  z = ~ Confirmed, text = ~hover, locations = ~abbr,
  color = ~ Confirmed, colors = 'Purples'
)
fig <- fig %>% colorbar(title = "Confirmed Cases")

fig <- fig %>% layout(
  title = paste0('Confirmed Cases, by State: ', date_latest),
  geo = g
)

fig
```
df <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/2014_world_gdp_with_codes.csv")
df


```{r}
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2014_world_gdp_with_codes.csv')


```

```{r}
glimpse(df)
```

```{r}
glimpse(daily)
```
```{r}
df <-
  df %>% 
  rename(land = COUNTRY)
```

```{r}
world <-
  daily %>% 
  rename(land = country_or_region) %>% 
  right_join(df, by = "land") %>% 
  select(Province_or_State, land, CODE, Confirmed, Deaths, Recovered, Active) %>% 
  mutate(hover = glue::glue(
    "{land}
     Deaths: {Deaths}
     Recovered:  {Recovered}"
  ))
```


```{r}
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2014_world_gdp_with_codes.csv')

# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

fig <- plot_geo(world)
fig <- fig %>% add_trace(
    z = ~ Confirmed, color = ~ Confirmed, colors = 'Greens',
    text = ~ hover, locations = ~ CODE, marker = list(line = l)
  )
fig <- fig %>% colorbar(title = 'COVID-19 Cases')
fig <- fig %>% layout(
    title = paste0('Global COVID-19 Confirmed Cases as of: ',
                   date_latest),
    geo = g
  )

fig
```