---
title: "Map_Work"
author: "Philipp Hoeper"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 2
---

```{r}
library(tidyverse)
library(glue)
library(plotly)
library(dygraphs)
library(xts)
library(reactable)
library(lubridate)
```

## Importing Data

```{r}
base_url <-
  paste0(
    "https://raw.githubusercontent.com/CSSEGISandData",
    "/COVID-19/master/csse_covid_19_data/",
    "csse_covid_19_daily_reports/"
  )

## currently just one day:
date_latest <-"04-30-2020"

extension <- ".csv"

url <- paste0(base_url, date_latest, extension)


```

COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series
https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series
base_url <-
  paste0('https://raw.githubusercontent.com/',
         'CSSEGISandData/COVID-19/master/',
         'csse_covid_19_data/csse_covid_19_time_series/')

## Importing time series data

```{r}
base_url <-
  paste0('https://raw.githubusercontent.com/CSSEGISandData',
    '/COVID-19/master/csse_covid_19_data/',
         'csse_covid_19_time_series/')

filename <- 
  paste0('time_series_covid19_', 
         c('confirmed_global', 'deaths_global', 'recovered_global'), '.csv')


url <- paste0(base_url, filename)
url
```


```{r}
Confirmed <- url[1] %>% 
  read_csv(col_types = cols(
    .default = col_double(),
    `Province/State` = col_character(),
    `Country/Region` = col_character()
  )) %>%
  rename(country_or_region = `Country/Region`)

Deaths <- url[2] %>% 
  read_csv(col_types = cols(
    .default = col_double(),
    `Province/State` = col_character(),
    `Country/Region` = col_character()
  )) %>%
  rename(country_or_region = `Country/Region`)

Recovered <- url[3] %>% 
  read_csv(col_types = cols(
    .default = col_double(),
    `Province/State` = col_character(),
    `Country/Region` = col_character()
  )) %>%
  rename(country_or_region = `Country/Region`)
```



## Manipulating Daily report data

```{r}
reactable::reactable(daily, searchable = TRUE,
                     pageSizeOptions = c(5, 10, 20), 
                     defaultPageSize = 5)
```
this data is for the US map which is not my focus but it is here for the sake of tips

```{r}
extra <- c(
  "Guam", "Grand Princess", "Virgin Islands, U.S.",
  "Diamond Princess", "Puerto Rico"
)
us <-
  us %>% 
  filter(!(Province_or_State %in% extra))
```

```{r}
data("statepop", package = "usmap")
glimpse(statepop)
```

```{r}
us <-
  us %>% 
  rename(full = Province_or_State) %>% 
  inner_join(statepop, by = "full") %>% 
  select(fips, abbr, full, Confirmed, Deaths, Recovered) %>% 
  mutate(hover = glue::glue(
    "{full}
     Deaths: {Deaths}
     Recovered:  {Recovered}"
  ))
```

Here is the states map once again just for reference a
```{r}
# give state boundaries a red border
lcol <- list(color = toRGB("red"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

fig <- plot_geo(us, locationmode = 'USA-states',
                marker = list(line = lcol))
fig <- fig %>% add_trace(
  z = ~ Confirmed, text = ~hover, locations = ~abbr,
  color = ~ Confirmed, colors = 'Purples'
)
fig <- fig %>% colorbar(title = "Confirmed Cases")

fig <- fig %>% layout(
  title = paste0('Confirmed Cases, by State: ', date_latest),
  geo = g
)

fig
```


## World Map

Lets download a data file that has the nations codes on it 
```{r}
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2014_world_gdp_with_codes.csv')


```
lets look at it
```{r}
glimpse(df)
```
for comparison lets look at the daily data set
```{r}
glimpse(daily)
```
just for the hell of it
```{r}
df <-
  df %>% 
  rename(land = COUNTRY)
```
now lets join the two and select the columns that we want, also make a hover tooltip

```{r}
daily <- read_csv(file = url) %>%
  rename(country_or_region = "Country_Region") %>%
  rename(Province_or_State = "Province_State") %>%
  group_by(country_or_region) %>%
  summarize(
    Deaths = sum(Deaths),
    Confirmed = sum(Confirmed),
    Recovered = sum(Recovered),
    Active = sum(Active)
  ) %>%
  rename(land = country_or_region) %>%
  mutate(
    land = plyr::mapvalues(
      land,
      from = c("US", "Taiwan*", "Bahamas", "Congo (Brazzaville)", "Congo (Kinshasa)", "	Gambia"),
      to = c("United States", "Taiwan", "Bahamas, The", "Congo, Republic of the", "Congo, Democratic Republic of the", "Gambia, The")
    )
  )
```
Now we have all the same country names apart from Swaziland which recently changed its name to Eswatini
So lets fix this

```{r}
df <-
  df %>% 
  mutate(
    land = plyr::mapvalues(
      land,
      from = c("Swaziland"),
      to = c("Eswatini")
    )
  ) 
```


```{r}
world <-
  daily %>% 
  right_join(df, by = "land") %>% 
  select(land, CODE, Confirmed, Deaths, Recovered, Active) %>% 
  mutate(hover = glue::glue(
    "{land}
     Deaths: {Deaths}
     Recovered:  {Recovered}"
  ))
```

Now plot time
```{r}
# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

fig <- plot_geo(world)
fig <- fig %>% add_trace(
    z = ~ Confirmed, color = ~ Confirmed, colors = 'Greens',
    text = ~ hover, locations = ~ CODE, marker = list(line = l)
  )
fig <- fig %>% colorbar(title = 'COVID-19 Cases')
fig <- fig %>% layout(
    title = paste0('Global COVID-19 Confirmed Cases as of: ',
                   date_latest),
    geo = g
  )

fig
```
As we can see, the map works!!

So thats recent data lets see how the map does over time lets repeat this process for different days 15 days apart

```{r}
date_latest2 <- "04-15-2020"
url2 <- paste0(base_url, date_latest2, extension)
daily2 <- read_csv(file = url2) %>%
  rename(country_or_region = "Country_Region") %>%
  rename(Province_or_State = "Province_State") %>%
  group_by(country_or_region) %>%
  summarize(
    Deaths = sum(Deaths),
    Confirmed = sum(Confirmed),
    Recovered = sum(Recovered),
    Active = sum(Active)
  ) %>%
  rename(land = country_or_region) %>%
  mutate(
    land = plyr::mapvalues(
      land,
      from = c("US", "Taiwan*", "Bahamas", "Congo (Brazzaville)", "Congo (Kinshasa)", "	Gambia"),
      to = c("United States", "Taiwan", "Bahamas, The", "Congo, Republic of the", "Congo, Democratic Republic of the", "Gambia, The")
    )
  )

world2 <-
  daily2 %>% 
  right_join(df, by = "land") %>% 
  select(land, CODE, Confirmed, Deaths, Recovered, Active) %>% 
  mutate(hover = glue::glue(
    "{land}
     Deaths: {Deaths}
     Recovered:  {Recovered}"
  ))
 
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

fig <- plot_geo(world2)
fig <- fig %>% add_trace(
    z = ~ Confirmed, color = ~ Confirmed, colors = 'Greens',
    text = ~ hover, locations = ~ CODE, marker = list(line = l)
  )
fig <- fig %>% colorbar(title = 'COVID-19 Cases')
fig <- fig %>% layout(
    title = paste0('Global COVID-19 Confirmed Cases as of: ',
                   date_latest2),
    geo = g
  )

fig
```


```{r}
date_latest3 <- "03-30-2020"
url3 <- paste0(base_url, date_latest3, extension)
daily3 <- read_csv(file = url3) %>%
  rename(country_or_region = "Country_Region") %>%
  rename(Province_or_State = "Province_State") %>%
  group_by(country_or_region) %>%
  summarize(
    Deaths = sum(Deaths),
    Confirmed = sum(Confirmed),
    Recovered = sum(Recovered),
    Active = sum(Active)
  ) %>%
  rename(land = country_or_region) %>%
  mutate(
    land = plyr::mapvalues(
      land,
      from = c("US", "Taiwan*", "Bahamas", "Congo (Brazzaville)", "Congo (Kinshasa)", "	Gambia"),
      to = c("United States", "Taiwan", "Bahamas, The", "Congo, Republic of the", "Congo, Democratic Republic of the", "Gambia, The")
    )
  )

world3 <-
  daily3 %>% 
  right_join(df, by = "land") %>% 
  select(land, CODE, Confirmed, Deaths, Recovered, Active) %>% 
  mutate(hover = glue::glue(
    "{land}
     Deaths: {Deaths}
     Recovered:  {Recovered}"
  ))
 
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

fig <- plot_geo(world3)
fig <- fig %>% add_trace(
    z = ~ Confirmed, color = ~ Confirmed, colors = 'Greens',
    text = ~ hover, locations = ~ CODE, marker = list(line = l)
  )
fig <- fig %>% colorbar(title = 'COVID-19 Cases')
fig <- fig %>% layout(
    title = paste0('Global COVID-19 Confirmed Cases as of: ',
                   date_latest3),
    geo = g
  )

fig
```


```{r}
date_latest4 <- "03-15-2020"
url4 <- paste0(base_url, date_latest4, extension)
daily4 <- read_csv(file = url4) %>%
  rename(country_or_region = "Country/Region") %>%
  rename(Province_or_State = "Province/State") %>%
  group_by(country_or_region) %>%
  summarize(
    Deaths = sum(Deaths),
    Confirmed = sum(Confirmed),
    Recovered = sum(Recovered)
  ) %>%
  rename(land = country_or_region) %>%
  mutate(
    land = plyr::mapvalues(
      land,
      from = c("US", "Taiwan*", "Bahamas", "Congo (Brazzaville)", "Congo (Kinshasa)", "	Gambia"),
      to = c("United States", "Taiwan", "Bahamas, The", "Congo, Republic of the", "Congo, Democratic Republic of the", "Gambia, The")
    )
  )

world4 <-
  daily4 %>% 
  right_join(df, by = "land") %>% 
  select(land, CODE, Confirmed, Deaths, Recovered) %>% 
  mutate(hover = glue::glue(
    "{land}
     Deaths: {Deaths}
     Recovered:  {Recovered}"
  ))
 
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

fig <- plot_geo(world4)
fig <- fig %>% add_trace(
    z = ~ Confirmed, color = ~ Confirmed, colors = 'Greens',
    text = ~ hover, locations = ~ CODE, marker = list(line = l)
  )
fig <- fig %>% colorbar(title = 'COVID-19 Cases')
fig <- fig %>% layout(
    title = paste0('Global COVID-19 Confirmed Cases as of: ',
                   date_latest4),
    geo = g
  )

fig
```
As we can see if we go back in time we see how the virus has spread over time. We cannot go much further back though without losing countries with no cases as seen in africa. But maybe we can fix this